---
title: "Case Study"
author: "Maya Krishnamoorthy"
date: "2024-10-08"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

# Specify figure sizes and specify theme options for ggplot
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load key packages.
```{r}
library(p8105.datasets)

data(nyc_airbnb)
```

## Brainstorm questions

* Where are max and min airbnb prices? 
  * What are average prices?
  * What factors affect prices?
```{r}
# Average prices
nyc_airbnb |> 
  summarize(
    min_price = min(price, na.rm = TRUE),
    max_price = max(price, na.rm = TRUE),
    avg_price = mean(price, na.rm = TRUE)
  )

# Avg price by borough and neighborhood
nyc_airbnb |> 
  group_by(neighbourhood_group, neighbourhood) |> 
  summarize(
    avg_price = mean(price, na.rm = TRUE)
  )

# Average price by borough
nyc_airbnb |> 
  group_by(neighbourhood_group) |> 
  summarize(
    avg_price = mean(price, na.rm = TRUE)
  )

# Graphical visualization of price distribution per borough
nyc_airbnb |> 
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram() +
  facet_grid(. ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0, 250))

# Does room type affect price
nyc_airbnb |> 
  group_by(room_type) |> 
  summarize(
    avg_price = mean(price, na.rm = TRUE)
  )

# Graphical visualization of price distribution per room type
nyc_airbnb |> 
  ggplot(aes(x = price, fill = room_type)) +
  geom_histogram(position = "dodge") +
  scale_x_continuous(limits = c(0, 250))
```


* Where are prices going up and down over time?
* What's the relationship between number of reviews and average reviews?
* Does room type affect availability?
* Are there repeat hosts?
  * If so, what does that mean?
  
```{r}
nyc_airbnb %>%
  filter(calculated_host_listings_count > 34) %>%
  distinct(host_id, host_name, calculated_host_listings_count)
```

* Where is the unit located?
  * What areas are popular?
```{r}
nyc_airbnb |> 
  group_by(neighbourhood_group, room_type) |> 
  summarize(mean_price = mean(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```

## Answeirng other questions

```{r}
nyc_airbnb |> 
  ggplot(aes(x = review_scores_location, y = price)) +
  geom_point()
```


Impact of borough on price -- Manhattan
```{r}
nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000) |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.2)
```

Summary table
```{r}
nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000, 
    room_type == "Entire home/apt") |> 
  group_by(neighbourhood) |> 
  summarize(mean_price = mean(price, na.rm = TRUE)) |> 
  arrange(desc(mean_price))
```

Visualization
```{r}
nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000, 
    room_type == "Entire home/apt") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

## Using leaflet

```{r}
library(p8105.datasets)
library(leaflet)
```


```{r}
pal <- colorNumeric(
  palette = "viridis", 
  domain = nyc_airbnb$review_scores_location)

nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000) |> 
  leaflet() |> 
  addTiles() |> 
  addCircleMarkers(~lat, ~long, color = ~ pal(review_scores_location), radius = 2)
```

